Appendix

### 2023-05-09 analysis/appendix.qmd
Link appendix targets to here

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(c(manuscript_nice, manuscript_manuscripty))
```

>>>>

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(c(appendix_nice, appendix_manuscripty))
```
